### 2020-12-24 about/vita.tex
Arithmetic subsequences

\leftright{\bf McGill University}{\bf September 2017 -- April 2021}
\leftright{\sl BSc, Honours Mathematics and Computer Science, minor Linguistics}{\sl Montr\'eal, QC, Canada}
CGPA: 3.79/4.
\medbreak
\leftright{\bf Charles University}{\bf February -- June 2019}
\leftright{\sl Exchange semester, Faculty of Mathematics and Physics}{\sl Prague, Czech Republic}
Grade: 1 on all courses (highest score attainable).

@@

\pubbegin S
\subitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton-Watson trees. {\sl arXiv preprint 2007.05681}.
Submitted July 2020.

>>>>

\leftright{\bf McGill University}{\bf September 2017 -- April 2021}
\leftright{\sl BSc, Honours Mathematics and Computer Science, minor Linguistics}{\sl Montr\'eal, QC, Canada}
CGPA: 3.81/4.
\medbreak
\leftright{\bf Charles University}{\bf February -- June 2019}
\leftright{\sl Exchange semester, Faculty of Mathematics and Physics}{\sl Prague, Czech Republic}
Grade: 1 on all courses (highest score attainable).

@@

\pubbegin S
\subitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton-Watson trees. {\sl arXiv preprint 2007.05681}.
Submitted July 2020.
\subitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set. {\sl arXiv preprint 2012.12339}.
Submitted December 2020.
